### 2023-12-04 manuscript.Rmd
Add appendix

classoption       : "man"
output            : papaja::apa6_pdf
repro:
  packages:
    - lavaan
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
    - aaronpeikert/repro@5a920f7
    - gert
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
---

@@

```{r, echo = FALSE, fig.width=11.3, fig.height=4.3, fig.align = 'center', fig.cap = "Simulation results: Estimated statistical power for recovering the data-generating model, i.e. Model 3 (y-axis) as a function of sample size (x-axis) with varying the factor inter-correlations when the loading strength was fixed to 0.7 (A) $;$ and with varying the loading strength when the factor inter-correlation was fixed to 0.3 (B). For each combination of parameters, 1,000 datasets were simulated. The red dashed horizontal line positioned at 95\\% discovery rate reflects the cut-off for identifying the appropriate sample size. The syntax to generate these plots with ggplot() can be found in the supplementary R Code on GitHub"}

@@

plot_load_model3 <- results_load_model3 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    linewidth = 1.3
  ) +
  xlab('Sample size') + ylab('Power (%)') + ggtitle('B \n') +
  scale_color_discrete('loading       \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

@@

plot_load_model1 <- results_load_model1 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A1 \n') +
  scale_color_discrete('loading    \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots

plot_load_model2 <- results_load_model2  %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A2 \n') +
  scale_color_discrete('loading \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots
plot_cov_model2 <- results_cov_model2 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('B2 \n') +
  scale_color_discrete('inter-factor \ncovariance') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0.0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots

@@

Note that in this tutorial, we limited our analyses to investigating the impact of either the separability of the theoretical constructs or the impact of the reliability of the estimates by keeping the other parameter constant throughout the simulation. The interaction of these parameters may differentially impact the resultant sample size estimates. However, a thorough investigation of the interaction of the two influencing factors would exponentially increase the number of conditions in a simulation. In our example on memory component processes we therefore confined our simulation to separate analyses in the interest of conciseness. For interested readers, two additional analyses on a) the effect of loading strength on estimates of power for higher levels of inter-factor correlation (0.7 as opposed to 0.3 in the original simulation) and b) the effect of inter-factor correlation on estimates of power for lower levels of factor-loadings (0.5 as opposed to 0.7 in the original simulation) can be found as supplementary material on the github repository. Given that previous work on memory development supports the assumption of reasonably high factor loadings and moderate inter-factor correlation in the present example, these additional analyses leave our conclusions unchanged.

@@

>>>>

classoption       : "man"
output            : papaja::apa6_pdf
appendix          : "Appendix.Rmd"

repro:
  packages:
    - lavaan
    - papaja
    - tidyverse
    - ggpubr
    - SimDesign
    - here
    - aaronpeikert/repro@5a920f7
    - gert
  tlmgr:
    - apa6
    - threeparttable
    - endfloat
    - framed
    - was
    - multirow
    - threeparttablex
    - environ
    - trimspaces
    - xpatch
    - csquotes
  scripts:
    - R/funs.R
---

@@

```{r, echo = FALSE, fig.width=11.3, fig.height=4.3, fig.align = 'center', fig.cap = "Simulation results: Estimated statistical power for recovering the data-generating model, i.e. Model 3 (y-axis) as a function of sample size (x-axis) with varying the factor inter-correlations when the loading strength was fixed to 0.7 (A) $;$ and with varying the loading strength when the factor inter-correlation was fixed to 0.3 (B). For each combination of parameters, 1,000 datasets were simulated. The red dashed horizontal line positioned at 95\\% discovery rate reflects the cut-off for identifying the appropriate sample size. The syntax to generate these plots with ggplot() can be found in the supplementary R Code on GitHub."}

@@

plot_load_model3 <- results_load_model3 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  geom_hline(
    yintercept = 95,
    linetype = "dashed",
    color = "#F29090",
    linewidth = 1.3
  ) +
  xlab('Sample size') + ylab('Power (%)') + ggtitle('B \n') +
  scale_color_discrete('Loading       \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 100),
    breaks = seq(0, 100, by = 20)
  ) +
  theme_plots

@@

plot_load_model1 <- results_load_model1 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A1 \n') +
  scale_color_discrete('Loading    \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots

plot_load_model2 <- results_load_model2  %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(loading_strength))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('A2 \n') +
  scale_color_discrete('Loading \nstrength') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots
plot_cov_model2 <- results_cov_model2 %>%
  ggplot(aes(sample_size, best_3 * 100, colour = factor(cov1))) +
  geom_point() +
  geom_line(alpha = 0.4,
            linewidth = 1.3,
            key_glyph = "rect") +
  xlab('Sample size') + ylab('Error Rate (%)') + ggtitle('B2 \n') +
  scale_color_discrete('Inter-factor \ncorrelation') +
  scale_x_continuous(
    expand = c(0, 0),
    limits = c(50, 200),
    breaks = seq(50, 200, by = 25)
  ) +
  scale_y_continuous(
    expand = c(0, 0),
    limits = c(0.0, 20),
    breaks = seq(0, 100, by = 5)
  ) +
  theme_plots

@@

Note that in this tutorial, we limited our analyses to investigating the impact of either the separability of the theoretical constructs or the impact of the reliability of the estimates by keeping the other parameter constant throughout the simulation. The interaction of these parameters may differentially impact the resultant sample size estimates. However, a thorough investigation of the interaction of the two influencing factors would exponentially increase the number of conditions in a simulation. In our example on memory component processes we therefore confined our simulation to separate analyses in the interest of conciseness. For interested readers, two additional analyses on a) the effect of loading strength on estimates of power for higher levels of inter-factor correlation (0.7 as opposed to 0.3 in the original simulation) and b) the effect of inter-factor correlation on estimates of power for lower levels of factor-loadings (0.5 as opposed to 0.7 in the original simulation) can be found in the appendix of this manuscript. Given that previous work on memory development supports the assumption of reasonably high factor loadings and moderate inter-factor correlation in the present example, these additional analyses leave our conclusions unchanged.

@@

# (APPENDIX) Appendix {-}

```{r child = "Appendix.Rmd"}
```
